Efficient Coalition Formation \\ for Web Services

### 2013-06-17 papers/coalition-journal-extension/coalition_journal.tex
A small info added to log
Changes

We discuessed $core$ as one the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community

>>>>

We discuessed $core$ as one the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap. One reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.

One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax. Another viable solution in our scenario is to stabilize the game using external subsidies. The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain. A community can subside the community with a contant coefficient value of $\lambda$. Rewarding a community with high number of quality participants with $\lambdav(C)$, where $\lambda \leq 1$. This can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods and have been .

Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators. These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.

The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. Communities can agree on However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community
